\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
% \usepackage{cite}
\usepackage{url}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{textcomp}
\usepackage{xcolor}
% \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage[sorting=none]{biblatex}
\addbibresource{biblio.bib}

% \def\thesection{\arabic{section}}

\begin{document}

\title{Assignment for the course \\Automated Planning Theory and Practice\\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Davide Lusuardi}
\IEEEauthorblockA{\textit{Department of information engineering and computer science} \\
\textit{University of Trento}\\
Trento, Italy \\
davide.lusuardi@studenti.unitn.it}
}

\maketitle

\begin{abstract}
This report is intended to present and analyze the assignment \cite{assignment} 
for the course \textit{Automated Planning Theory and Practice}
and discuss some design choices regarding its modelling and implementation.

The assignment is inspired by an emergency services logistics scenario where
a set of robotic agents have the task to deliver crates containing emergency 
supplies to some injured people.

The assignment is divided into four subproblems, each building on the previous 
one with increasing complexity.
In the first problem, the robot can pick up and move just one crate at time.
In the second problem, the complexity increases a bit given that the robot
exploits a carrier that can load up to four crates.
In the third problem, it is required to use durative actions in order to assign
reasonable duration to different actions and model which actions can be executed
in parallel.
Lastly, the third problem has to be implemented within the \texttt{PlanSys2} 
framework, executing the plan in a simulated environment.

In this report, we show how these problems can be formalized using the PDDL planning
language and solved by state-of-the-art planners.

\end{abstract}

% \begin{IEEEkeywords}
% component, formatting, style, styling, insert
% \end{IEEEkeywords}

\input{sec01_introduction.tex}
\input{sec02_understanding.tex}
\input{sec03_design_choices.tex}
\input{sec04_results.tex}
\input{sec05_conclusions.tex}




% \bibliographystyle{IEEEtran}
% \bibliography{biblio}

\printbibliography %Prints bibliography

\end{document}